---
title: "data analysis"
author: "Robert Kettenstock"
date: "11/27/2018"
output: html_document
---

```{r}
View(eights2)
```


```{r}
eights2$V4 <- eights2$V4 + 2.5
weights <- eights2[,4]
weights2 <- as.numeric(as.character(weights))
mean(weights2)
weightavg_late <- mean(weights2[1:184],na.rm=T)
weightavg_early <- mean(weights2[185:384], na.rm=T)
```

assign "weights" to be the fourth column of the eights2 dataset
assign "weights2" to be the numeric values of weights
mean of weights2 displays the mean for the whole column
"weightavg_late" and "weightavg_early" becomes the mean of rows 1-184 and 185-384 respectively
na.rm is accounting for NA values that we have

```{r}
weightavg_early
```

```{r}
weightavg_late
```

```{r}
weight_late <- eights2[1:184,4]
weight_early <- eights2[185:384,4]
```


```{r}
weight_late <- as.numeric(as.character(weight_late))
weight_early <- as.numeric(as.character(weight_early))
boxplot(weight_late, weight_early, main = "Weight of seeds of Early vs Late Populations", ylab = "Late      Early", xlab = "Weight (g)", varwidth = TRUE, horizontal = TRUE)
```

creates a boxplot that consists of the numeric values in weight_early and weight_late, flipped horizontally

```{r}
grep("Yellow", eights2$V1)
cnt <- 1
for (i in eights2$V1) {
  cnt <- cnt + 1
  if(cnt > 1 && cnt < 386) {
    print(grep("Yellow", i))
  } else {break}
}
```

pattern: "Yellow", "Pink", "Orange", "Avocado"
"A" - "H"
x: eights2
weights: $V4

```{r}
average <- function(x){
  sum.value <- 0
  i <- 1
  while ( i <= length(x)){
    sum.value = sum.value + x[i]
    i <- i + 1
  }
  avg <- sum.value/length(x)
  return(avg)
}
```

mean divide sum.value by i

```{r}
grep("Yellow", eights2$V1)
Yellow_Rows <- grep("Yellow", eights2$V1)

eights2$V4 <- as.numeric(as.character(eights2$V4))
```


```{r}
Yellow_Weight <- seq(1:length(Yellow_Rows))
for (p in seq(1:length(Yellow_Rows))) {
  for (i in Yellow_Rows) {
  Yellow_Weight[[p]] <- eights2[i, 4]
  }}

Yellow_Weight
for (i in Yellow_Rows) {
  assign(eights2[i, 4], Yellow_Weight[i,])

}
for (p in seq(1:96)) {
  print(p)
}
```


```{r}
x[[5]] <- 26
x
```

```{r}
Yellow_Weight <- numeric(length(Yellow_Rows))
for(i in seq(along=Yellow_Weight)) {
	Yellow_Weight[i] <- as.numeric(eights2[i,4])
}
Yellow_Weight

for(i in Yellow_Rows) {
  print(i)
}

```

```{r}
eights2[-c(1),]
eights2 <- eights2[-c(1),]
eights3 <- eights2[order(eights2$V1),]
#correct seed weight

View(eights3)

```


```{r}
rownames(eights3) <- NULL
new_weights <- eights3[,4]
new_weights2 <- as.numeric(as.character(new_weights))
mean(new_weights2)
weightavg_Yellow <- mean(new_weights2[289:384],na.rm=T)
weightavg_Pink <- mean(new_weights2[193:288], na.rm=T)
weightavg_Orange <- mean(new_weights2[97:192], na.rm=T)
weightavg_Avocado <- mean(new_weights2[1:96], na.rm=T)

```

```{r}
Weight_Yellow <- eights3[289:384,4]
Weight_Orange <- eights3[97:192,4]
Weight_Pink <- eights3[193:288,4]
Weight_Avocado <- eights3[1:96,4]

```

```{r}
Weight_Yellow <- as.numeric(as.character(Weight_Yellow))
Weight_Pink <- as.numeric(as.character(Weight_Pink))
Weight_Orange <- as.numeric(as.character(Weight_Orange))
Weight_Avocado <- as.numeric(as.character(Weight_Avocado))
```

```{r}
boxplot(Weight_Yellow, Weight_Pink, Weight_Avocado, Weight_Orange, names=c("Yellow", "Pink", "Avocado", "Orange"), main= "RAD-seq Growth Room Seed Weights", ylab= "Seed Weights (g)", xlab= "Shelf", col = c("yellow", "deeppink1", "olivedrab3", "orange"))
```


